### 2019-11-25 paper/conclusion.tex

\section{Conclusion} \label{Conclusion}
Five initial fissile loadings strategies have been studied for 
transitioning to the thorium fuel cycle in the Single-fluid Double-zone 
Thorium-based Molten Salt Reactor (SD-TMSR). We 
adopted two different feed mechanisms: thorium and non-thorium. 
This work determined that High Assay Low Enriched Uranium (HALEU), even with some Pu, is infeasible. 
Full lifetime (60 year) depletion for the whole-core SD-TMSR model was 
performed with reactor-grade Pu, TRU, and $^{233}$U as initial fissile 
materials. Additionally, the dynamics of the effective multiplication factor 
$k_{eff}$, major isotopes mass, neutron energy spectrum, and essential safety 
parameters have been investigated.

@@

\section{Future work}
The authors intend to verify obtained results using another tool: batch-wise 
code SaltProc \cite{rykhlevskii_arfc/saltproc_2018,rykhlevskii_milestone_2019}.
In further simulations, we intend to account for delayed 
neutron precursor drift. The \gls{SD-TMSR} reactivity control system has not 
been introduced in the literature yet. Thus, the control rod design and 
configuration may be suggested in the nearest future.

An additional area to explore is the accident safety analysis which 
requires high-fidelity multi-physics simulation of the \gls{SD-TMSR} with the 
coupled neutronics/thermal-hydraulics software, Moltres 
\cite{lindsay_introduction_2018}. The full-core SERPENT-2 model of the 
\gls{SD-TMSR} and equilibrium fuel salt compositions, obtained in this work, 
will be employed to generate problem-oriented nuclear data libraries for 
Moltres. The ultimate goal of this effort is to develop a 
fast-running computational model for studying the dynamic behavior of generic 
\glspl{MSR}, performing safety analysis for different accident scenarios, and 
optimizing the design of various reactor concepts.

>>>>

\section{Conclusion} \label{Conclusion}
Five initial fissile loadings strategies have been studied for 
transitioning to the thorium fuel cycle in the Single-fluid Double-zone 
Thorium-based Molten Salt Reactor (SD-TMSR). We 
adopted two different feed mechanisms: thorium and non-thorium. 
This work determined that High Assay Low Enriched Uranium (HALEU), even mixed with Pu, is infeasible. 
Full lifetime (60 year) depletion for the whole-core SD-TMSR model was 
performed with reactor-grade Pu, TRU, and $^{233}$U as initial fissile 
materials. Additionally, the dynamics of the effective multiplication factor 
$k_{eff}$, major isotopes mass, neutron energy spectrum, and essential safety 
parameters have been investigated.

@@

\section{Future work}
The authors intend to verify obtained results using another tool: batch-wise 
code SaltProc \cite{rykhlevskii_arfc/saltproc_2018,rykhlevskii_milestone_2019}.
Additionally, the accident safety analysis using coupled 
neutronics/thermal-hydraulics software, Moltres 
\cite{lindsay_introduction_2018} will be performed. The full-core SERPENT-2 
model of the \gls{SD-TMSR} and equilibrium fuel salt compositions, obtained in 
this work, will be employed to generate problem-oriented nuclear data 
libraries for Moltres. The ultimate goal of this effort is to develop a 
fast-running computational model for studying the dynamic behavior of generic 
\glspl{MSR}, performing safety analysis for different accident scenarios, and 
optimizing the design of various reactor concepts.
